Counterfactual Training

### 2024-12-18 paper/presenations/slides.qmd
not sure why sequentially doesn't work

>>>>

## Problems on Cluster

- Trying to distribute: 
    1. Models/experiments across processes and then ...
    2. ... for each model/experiment distribute the counterfactual search across processes.
- Out-of-memory issues, data races, ...
- When using multi-processing for models and multi-threading for counterfactual search, I get low CPU efficiency on DelftBlue (jobs get cancelled).
